When are Fuzzy Extractors Possible?

### 2015-02-10 trunk/info-bounds/FuzzyExtPossibility.tex
revisions in body on notation and theme

\begin{abstract}
Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key. A minimum condition for the security of the key is the hardness of guessing a value that is similar to the secret, because the fuzzy extractor converts such a guess to the key.
We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.  Fuzzy min-entropy measures the success of the adversary when provided with the functionality of the fuzzy extractor.  It measures the \emph{ideal} security of a distribution.

High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required (assuming the existence of semantically-secure graded encodings). Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy. The challenge is to design information-theoretic fuzzy extractors whose security (almost) matches the fuzzy min-entropy of a distribution.

In this work, we ask whether this challenge is inherent.
 We provide two main technical results.
\begin{itemize}
\item \textbf{Sufficiency of fuzzy min-entropy:}  It is possible to build a fuzzy extractor for any \emph{precisely known} physical source.  This result justifies fuzzy min-entropy as the right measure of the quality of a noisy distribution for key derivation.  Previous results considered the entropy and error tolerance of a separately and had not secured many sources with fuzzy min-entropy.
\item \textbf{Cost of distributional uncertainty:}  High entropy distributions can never be fully observed and must be modeled.  An adversary may have a better model than the fuzzy extractor designer.  To compensate, fuzzy extractors are typically designed to work for families of physical sources. We show that this uncertainty is an impediment to security by building a family of high fuzzy min-entropy sources for which no fuzzy extractor can exist.  This result justifies further study of physical sources to increase the fidelity of our models.
\end{itemize}
We provide similar but stronger results for secure sketches, whose goal is not to derive a consistent key, but to recover a consistent reading of the secret.  Our results are information-theoretic, but we discuss implications for the computational setting.

@@

Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.  Superlogarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition).  Fuzzy min-entropy measures the maximum obtainable key from a noisy distribution.  
However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.\footnote{For nearly uniform distributions, $\Hfuzz(W) \approx \Hoo(W)- \log |B_t|$.  In this setting, standard coding based constructions of fuzzy extractors (instantiated with optimum codes) yield keys of size approximately $\Hfuzz(W)$.}  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.

We answer this question in two important settings.  An important aspect of a fuzzy extractor is how much it knows about the target distribution $W$.  In the extreme the fuzzy extractor has a complete description of the probability density function of $W$.  We call this setting the \emph{known distribution} setting.  (Previous works have consider

Assuming full knowledge of a distribution is often unrealistic. Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled. It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary, with greater resources, would likely be able to build a better model. Therefore, fuzzy extractor designs cannot usually be tailored to one  particular source. Existing designs work for a family of sources (for example, all sources of min-entropy at least $m$ with at most $t$ errors). Thus, the design is fixed with a partially known distribution, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.  We call this setting \emph{family of distributions}.
We ask whether fuzzy min-entropy is sufficient in each of these settings.

\paragraph{Sufficiency of $\Hfuzz(W)$ for a Known Distribution}
We show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a \emph{known distribution} $W$.  It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).

A number of previous works in this known-distribution setting have provided efficient algorithms and
tight bounds for specific distributions---generally the uniform distribution or
i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
Our characterization may be seen as unifying previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.

\paragraph{Impossibility of a Fuzzy Extractor for a Family of Distributions}
Our results are negative when the distribution $W$ is only known to come from a family $\mathcal{W}_Z$ (\thref{thm:imposs fuzz ext}).
Specifically, we show a family of distributions $\mathcal{W}_Z$ such that not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}_Z$.  We emphasize that each distribution $W_z\in \mathcal{W}_Z$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W_z)=\Hoo(W_z)$, because all points in $W_z$ are distance at least $t$ apart. Our proof relies on high dimensionality of each $W_z$ and on perfect correctness of the $\rep$ procedure.
This result shows that uncertainty in the distribution $W$ is devastating to building a fuzzy extractor.  This result motivates the further research into physical sources.  \bnote{come back to this sentence}

\begin{table}[h]
\begin{center}
\begin{tabular}{c  l l }
 & Known Distribution & Family of Distributions\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext})\\
\hline
Secure Sketch & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs sketch})
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a superlogarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}

@@

\bnote{asked to discuss implications of our negative results}
\bnote{can we reframe the paper as the cost of distributional uncertainty?}
\bnote{compare to current constructions?}
\subsection{Our Techniques}

\paragraph{Techniques for Positive Results for Known Distributions} We now explain how to construct a secure sketch for an arbitrary known distribution $W$ (we already explained how to construct a fuzzy extractor from it).  We begin with distributions in which all points in the support have the same probability (so-called ``flat'' distributions).   Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must disambiguate which point $w\in W$ within distance $t$ of $w'$ was sketched. Disambiguating multiple points can be accomplished by universal hashing, as long as the size of hash output space is slightly greater than the number of possible points. Thus, our sketch is computed via a universal hash of $w$. To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$. Because the distribution is flat, it is also the ball with the most points of nonzero probability. Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball. Since $\Hfuzz(W)$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz(W)$.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ``levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

\paragraph{Techniques for Negative Results for Distribution Families}
We construct a family of distributions $\mathcal{W}_Z$ and prove impossibility for a uniformly random $W_z \leftarrow \mathcal{W}_Z$~(instead of proving impossibility for a worst-case $W_z$).
We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W_z\leftarrow \mathcal{W}_Z$ and $w\leftarrow W_z$), while
the adversary knows $W_z$.   To exploit the asymmetry, we construct $\mathcal{W}_Z$ so that conditioning on the knowledge of $W_z$~(the outcome $z$) reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on a large fraction of the entire space.

@@

The result for fuzzy extractors is delicate.  It uses the fact that $p$ partitions the space into nonoverlapping regions, which is implied by perfect correctness.  Extending this result to imperfect correctness seems challenging and is an interesting open problem. It also uses the fact that there are few points far from the boundary of every region, which is implied by the geometry of  the high-dimensional Hamming space.  This fact seems crucial: in contrast, in low-dimensional Euclidean space, which does not have this property, a single fuzzy extractor can work for any distribution with sufficient $\Hfuzz$. (Such a construction would use quantization or tiling, similar to, for example, \cite{CK03,LT03,CZC04,LC06,BDHTV10,VTOSS10}.  Each sample from $W$ would map to the ``tile'' containing it, from which the output key would be extracted. A randomly chosen quantizer would have the property that few samples lie near the boundary, giving almost-perfect correctness; if perfect correctness is desired, we can give up on security for those rare samples and simply use a special value of $p$ to indicate that one of them was the input.)

\subsection{Related Settings}
\label{sec:related settings}
\paragraph{Other settings with close readings:  $\Hfuzz$ is sufficient}
The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.   In this computational setting, fuzzy extractors and secure sketches can be constructed for the family of all distributions $W$ with superlogarithmic $\Hfuzz$ by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}. The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.  In addition to relying on strong assumptions for security (namely, the existence of semantically-secure multilinear maps), this construction is not of practical efficiency. Note that if this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).

@@

\paragraph{Correlated rather than close readings}
A different model for the problem of key derivation from noisy sources does not explicitly consider the distance between $w$ and $w'$, but rather views $w$ and $w'$ as samples of drawn from a correlated pair of random variables.   This model is considered in multiple works, including~\cite{wyner1975wire,DBLP:journals/tit/CsiszarK78,DBLP:journals/tit/AhlswedeC93,DBLP:journals/tit/Maurer93}; recent characterizations of when key derivation is possible in this model include \cite{DBLP:conf/asiacrypt/RennerW05} and \cite{DBLP:journals/corr/TyagiW14}.  We compare our positive results to these characterizations in \apref{sec:corr variables}.  To the best of our knowledge, prior results on correlated random variables are in the known distribution setting, we are unaware of works that consider security for a family of distributions.

@@

\paragraph{Organization} The remainder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:known distributions}, we construct a fuzzy extractor for each known distribution with fuzzy min-entropy.  In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we provide negative results  for families of distributions for secure sketches and fuzzy extractors, respectively.

@@

In this section, we define fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with modifications.  First we allow for error, as discussed in \cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}.  Second, in the \emph{family of distributions} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
%This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  
%We discuss known distribution algorithms in \secref{sec:known distributions def}.  
Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $\key \in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then $\Pr[\rep(w', p) = \key] \geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins on $\gen$ and $\rep$, but $w'$ cannot be a function of $p$).
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(\Key,P)\leftarrow\gen (W)$, then $\sd((\Key,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

\noindent
Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.  The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness}) and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.  \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.  \rec takes an element $w'\in\mathcal{M}$ and $ss\in\{0,1\}^*$.  $(\sketch, \rec)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins of $\sketch$ and $\rec$, but $w'$ cannot be a function of $\sketch(w)$).
\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}

@@

\paragraph{The Case of Known Distribution}
If in the above definitions we take $\mathcal{W}$ to be a one-element set containing a single distribution $W$, then the fuzzy extractor/secure sketch is said to be constructed for a \emph{known distribution}.  In this case, we need to require correctness only for $w$ that have nonzero probability\footnote{We can extend correctness to all of $\mathcal{M}$ by defining $\gen$/$\sketch$ to output the point $w$ as part of $p/ss$ on zero-probability inputs, which will ensure that $\rep$/$\rec$ can always be correct; this does not affect security.}.

@@

\begin{lemma}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon)$-average case extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
\end{itemize}
\end{lemma}

@@

\noindent
\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is 
$
\Hav(W |\sketch(W)) = \Hoo(W) - \log \beta_{t} - \omega(\log n).
$
For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.

>>>>

\begin{abstract}
Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key. A minimum condition for the security of the key is the hardness of guessing a value that is similar to the secret, because the fuzzy extractor converts such a guess to the key.
We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.  Fuzzy min-entropy measures the success of the adversary when provided with \emph{only} the functionality of the fuzzy extractor and thus the \emph{ideal} security possible from a noisy distribution.

High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required. Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy. The challenge is to design information-theoretic fuzzy extractors whose security (almost) matches the fuzzy min-entropy of a distribution.
In this work, we ask whether this challenge is inherent.
 We provide two main technical results.
\begin{itemize}
\item \textbf{Sufficiency of fuzzy min-entropy:}  We construct a fuzzy extractor for each physical source with fuzzy min-entropy.  This result justifies fuzzy min-entropy as the right measure of the quality of a noisy distribution for key derivation.  Previous results considered the entropy and error tolerance of a separately and had not secured many sources with fuzzy min-entropy.  The constructed fuzzy extractor must \emph{precisely know} the distribution of the noisy source.
\item \textbf{Cost of distributional uncertainty:}  High entropy sources can never be fully observed and must be modeled.  An adversary may have a better model than the fuzzy extractor designer.  To compensate, fuzzy extractors are typically designed to work for families of physical sources. We show that this uncertainty is an impediment to security by building a family of high fuzzy min-entropy sources for which no fuzzy extractor can exist.  This result emphasizes the importance of high fidelity models of high entropy sources.
\end{itemize}
We provide similar but stronger results for secure sketches, whose goal is not to derive a consistent key, but to recover a consistent reading of the secret.  Our results are information-theoretic, but we discuss implications for the computational setting.

@@

Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.  It can be thought of as measuring the ideal security of a noisy source of entropy when used for key derivation.  This is similar to how security is measured for program obfuscation~\cite{barak2001possibility}, we discuss the connection to program obfuscation in \secref{sec:related settings}.  Superlogarithmic fuzzy min-entropy is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition).

However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.\footnote{For nearly uniform distributions, $\Hfuzz(W) \approx \Hoo(W)- \log |B_t|$.  In this setting, standard coding based constructions of fuzzy extractors (instantiated with optimum codes) yield keys of size approximately $\Hfuzz(W)$.}  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}. We provide an answer in two settings.

\paragraph{Sufficiency of $\Hfuzz(W)$ for a Precisely Known Distribution}
Ideally, a fuzzy extractor has \emph{precise knowledge} of the probability distribution function of $W$.  We call this  the \emph{precise knowledge} setting.  In this setting, we show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}). Our construction crucially utilizes the probability distribution function of $W$ and, in particular, is not polynomial time.  This result shows that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor of a distribution $W$.

A number of previous works in the precise knowledge setting have provided efficient algorithms and
tight bounds for specific distributions---generally the uniform distribution or
i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
Our characterization unifies previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.

\paragraph{The Challenge of Precisely Knowing a High Entropy Distribution}
Assuming \emph{precise knowledge} of a distribution $W$ may be unrealistic. Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled. It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary, with greater resources, would likely be able to build a better model. Therefore, fuzzy extractor designs cannot usually be tailored to one  particular source. Existing designs work for a family of sources (for example, all sources of min-entropy at least $m$ with at most $t$ errors). Thus, the design is fixed with a partially known distribution, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.  We call this setting \emph{distributional uncertainty}.
We ask whether fuzzy min-entropy is sufficient in each of these settings.

\paragraph{The Cost of Distributional Uncertainty}
When the distribution is $W$ is uncertain, our results are negative.   In this setting, $W$ is only known to be in family of distributions $\mathcal{W}_Z$.
We construct a family $\mathcal{W}_Z$ where not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}_Z$.  We emphasize that each distribution $W_z\in \mathcal{W}_Z$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W_z)=\Hoo(W_z)$, because all points in $W_z$ are distance at least $t$ apart. Our proof relies on high dimensionality of each $W_z$ and on perfect correctness of the $\rep$ procedure.
This result shows that uncertainty in the distribution $W$ is devastating to building a fuzzy extractor.  In particular, our positive results (\corref{cor:extension to fuzz ext}) show it is possible to build a fuzzy extractor for each $W_z$, but no construction can simultaneously secure the whole family.  Our result motivates further research into high fidelity descriptions of noisy physical sources.

\begin{table}[h]
\begin{center}
\begin{tabular}{c  l l }
 & Precise Knowledge & Distributional Uncertainty\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext})\\
\hline
Secure Sketch & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs sketch})
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a superlogarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}

@@

\bnote{compare to current constructions?}
\subsection{Our Techniques}

\paragraph{Techniques for Positive Results for a Precisely Known Distribution} We now explain how to construct a secure sketch for a precisely known distribution $W$ with fuzzy min-entropy (we already explained how to construct a fuzzy extractor from it).  We begin with distributions in which all points in the support have the same probability (so-called ``flat'' distributions).   Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must disambiguate which point $w\in W$ within distance $t$ of $w'$ was sketched. Disambiguating multiple points can be accomplished by universal hashing, as long as the size of hash output space is slightly greater than the number of possible points. Thus, our sketch is computed via a universal hash of $w$. To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$. Because the distribution is flat, it is also the ball with the most points of nonzero probability. Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball. Since $\Hfuzz(W)$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz(W)$.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ``levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}~(\consref{cons:leveling}).

\paragraph{Techniques for Negative Results for Distributional Uncertainty}
We construct a family of distributions $\mathcal{W}_Z$ and prove impossibility for a uniformly random $W_z \leftarrow \mathcal{W}_Z$.
We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W_z\leftarrow \mathcal{W}_Z$ and $w\leftarrow W_z$), while
the adversary knows $W_z$.   To exploit the asymmetry, we construct $\mathcal{W}_Z$ so that conditioning on the knowledge of $W_z$~(the outcome $z$) reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on a large fraction of the entire space.

@@

The result for fuzzy extractors is delicate.  It uses the fact that $p$ partitions the space into nonoverlapping regions, which is implied by perfect correctness.  Extending this result to imperfect correctness seems challenging and is an interesting open problem. Our result also uses the fact that there are few points far from the boundary of every region, which is implied by the geometry of  the high-dimensional Hamming space.  This fact seems crucial: in contrast, in low-dimensional Euclidean space, which does not have this property, a single fuzzy extractor can work for any distribution with sufficient $\Hfuzz$. (Such a construction would use quantization or tiling, similar to, for example, \cite{CK03,LT03,CZC04,LC06,BDHTV10,VTOSS10}.  Each sample from $W$ would map to the ``tile'' containing it, from which the output key would be extracted. A randomly chosen quantizer would have the property that few samples lie near the boundary, giving almost-perfect correctness; if perfect correctness is desired, we can give up on security for those rare samples and simply use a special value of $p$ to indicate that one of them was the input.)

\subsection{Related Settings}
\label{sec:related settings}
\paragraph{Other settings with close readings:  $\Hfuzz$ is sufficient}
The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.   In this computational setting, a single fuzzy extractor (or secure sketch) can simultaneously secure all possible distributions by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}. The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.  This construction is secure when the adversary can rarely learn \key with oracle access to the program functionality.  The set of distributions with fuzzy min-entropy are exactly those where an adversary learns \key with oracle access to the functionality with negligible probability.\footnote{If this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).  Extending our negative result to the computational setting would rule out the existence of semantically-secure multilinear maps.}

@@

\paragraph{Correlated rather than close readings}
A different model for the problem of key derivation from noisy sources does not explicitly consider the distance between $w$ and $w'$, but rather views $w$ and $w'$ as samples of drawn from a correlated pair of random variables.   This model is considered in multiple works, including~\cite{wyner1975wire,DBLP:journals/tit/CsiszarK78,DBLP:journals/tit/AhlswedeC93,DBLP:journals/tit/Maurer93}; recent characterizations of when key derivation is possible in this model include \cite{DBLP:conf/asiacrypt/RennerW05} and \cite{DBLP:journals/corr/TyagiW14}.  We compare our positive results to these characterizations in \apref{sec:corr variables}.  To the best of our knowledge, prior results on correlated random variables are in the precise knowledge setting, we are unaware of works that consider implications of distributional uncertainty.

@@

\paragraph{Organization} The remainder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:known distributions}, we construct a fuzzy extractor in the precise knowledge setting.  In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we construct families of distributions that no secure sketches and fuzzy extractors can secure, respectively~(the distributional uncertainty setting).

@@

In this section, we define fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with modifications.  First, we allow for error as discussed in \cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}.  Second, in the \emph{distributional uncertainty} setting we consider a general family $\mathcal{W}_Z$ of distributions instead of families containing all distributions of a given min-entropy.
%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
%This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  
%We discuss known distribution algorithms in \secref{sec:known distributions def}.  
Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}_Z, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $\key \in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then $\Pr[\rep(w', p) = \key] \geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins on $\gen$ and $\rep$, but $w'$ cannot be a function of $p$).
\item \emph{Security:} for any distribution $W_z\in\mathcal{W}_Z$, if $(\Key,P)\leftarrow\gen (W_z)$, then $\sd((\Key,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

\noindent
Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.  The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness}) and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}_Z, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.  \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.  \rec takes an element $w'\in\mathcal{M}$ and $ss\in\{0,1\}^*$.  $(\sketch, \rec)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins of $\sketch$ and $\rec$, but $w'$ cannot be a function of $\sketch(w)$).
\item \emph{Security}: for any distribution $W_z\in\mathcal{W}_Z$, $\Hav(W_z|\sketch(W_z))\geq \tilde{m}$.
\end{enumerate}
\end{definition}

@@

\paragraph{The Case of a Precisely Known Distribution}
If in the above definitions we take $\mathcal{W}_Z$ to be a one-element set containing a single distribution $W$, then the fuzzy extractor/secure sketch is said to be constructed for a \emph{precisely known distribution}.  In this case, we need to require correctness only for $w$ that have nonzero probability\footnote{We can extend correctness to all of $\mathcal{M}$ by defining $\gen$/$\sketch$ to output the point $w$ as part of $p/ss$ on zero-probability inputs, which will ensure that $\rep$/$\rec$ can always be correct; this does not affect security.}.

@@

\begin{lemma}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, \mathcal{W}_Z, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon)$-average case extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, \mathcal{W}_Z, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
\end{itemize}
\end{lemma}

@@

\noindent
\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is $\Hav(W |\sketch(W)) = \Hoo(W) - \log \beta_{t} -\log 1/\delta$. For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.
